---
title: "Stimulant project"
author: "Adam Kaminski"
date: "2023-05-12"
output:
  pdf_document: default
  word_document: default
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(knitr)
require(gt)
```

# <br>
## Data processing

#### Options
##### Inclusion criteria selection
##### Decision to combine certain cortical functional networks
```{r}
# user inputs
# - inclusion criteria
#     ... 1 = KSADS + rs-fMRI
#     ... 2 = CBCL + rs-fMRI
#     ... 3 = KSADS + CBCL + rs-fMRI

ksadscrit <- "KSADS (ADHD present at baseline)"
cbclcrit <- "CBCL (>=60 on ADHD problems DSM-oriented scale)"
rsfmricrit <- "rs-fMRI recommended use (baseline and year 2)"

inclcrit <- 3

if(inclcrit==3){writeLines(paste("Inclusion criteria:\n-",ksadscrit,"\n-",cbclcrit,"\n-",rsfmricrit,sep=" "))}

# - Combine certain cortical functional networks?
#     ... 1 = yes
#     ... 0 = no
combine <- 1

if(combine==1){writeLines("Averaging cingulo-opercular + salience and somatomotor hand + somatomotor mouth networks")}

```

## <br>
#### KSADS
##### From NDADownloadManager
##### Exclude individual if ADHD is not present at baseline
```{r, warning=FALSE}

setwd("/Users/adamkaminski/Desktop/stimproj/data/ABCD_data/")
ksads <- read.csv('abcd_ksad01_adhd_present.csv')
ksads <- ksads[,-2:-3]
ksads <- reshape(ksads, idvar = "ID", timevar = "time", direction = "wide")
origlen <- dim(ksads)[1]
ksads <- ksads[,-3:-4]
ksads <- ksads[ksads$adhd_present.0==1,]
ksads <- ksads[complete.cases(ksads), ]

writeLines(paste("Starting n (i.e., people with KSADS data): ",origlen,"\nOutcome: ",dim(ksads)[1]," people have ADHD at baseline according to KSADS",sep=""))

```

## <br>
#### Recommended rs-FC data use
##### From NDADownloadManager
##### Exclude individual if rs-fMRI data is not recommended at baseline or the year 2 timepoint
```{r, warning=FALSE}
setwd("/Users/adamkaminski/Desktop/stimproj/data/ABCD_data/")
imgincl <- read.csv('abcd_imgincl01_rsfmri.csv')
imgincl <- imgincl[,-2:-3]
imgincl <- reshape(imgincl, idvar = "ID", timevar = "time", direction = "wide")
origlen <- dim(imgincl)[1]
imgincl <- imgincl[imgincl$imgincl_rsfmri_include.0==1,]
imgincl <- imgincl[imgincl$imgincl_rsfmri_include.2==1,]
imgincl <- imgincl[complete.cases(imgincl), ]

writeLines(paste("Starting n (i.e., people with rs-fMRI data): ",origlen,"\nOutcome: ",dim(imgincl)[1]," people have recommended rs-fMRI data at baseline and the year 2 timepoint",sep=""))

```

## <br>
#### CBCL
##### From NDADownloadManager
##### Exclude individual if t-score on the DSM-oriented ADHD problems scale < 60 at baseline
```{r, warning=FALSE}
setwd("/Users/adamkaminski/Desktop/stimproj/data/ABCD_data/")
cbcl <- read.csv('./abcd_cbcls01.csv')
cbcl <- cbcl[cbcl$time=="baseline_year_1_arm_1",]
origlen <- dim(cbcl)[1]
cbcl <- cbcl[cbcl$ADHD.CBCL.DSM5.Scale..t.score.>=60,]

writeLines(paste("Starting n (i.e., people with cbcl baseline data): ",origlen,"\nOutcome: ",dim(cbcl)[1]," people have t-scores 60 or above on the DSM-oriented ADHD problems scale at baseline",sep=""))

```

## <br>
#### Determine individuals who meet combinations of criteria (KSADS, rs-fMRI, CBCL)
```{r, warning=FALSE}

ncrits <- matrix(0,3,1)
overlap1 <- imgincl$ID[imgincl$ID%in%ksads$ID]
ncrits[1,1] <- length(overlap1)
overlap2 <- cbcl$ID[cbcl$ID%in%imgincl$ID]
ncrits[2,1] <- length(overlap2)
overlap3 <- imgincl$ID[imgincl$ID%in%ksads$ID]
overlap3 <- cbcl$ID[cbcl$ID%in%overlap3]
ncrits[3,1] <- length(overlap3)
colnames(ncrits) <- "n"
rownames(ncrits) <- c("KSADS + rs-fMRI recommeded use","CBCL + rs-fMRI recommeded use","KSADS + CBCL + rs-fMRI recommeded use")

gt(as.data.frame(ncrits),
   rownames_to_stub = TRUE)

# # # # # # # # # # # # # # # # # # # # # # #
# !!! Below depends on user input above !!! #
# # # # # # # # # # # # # # # # # # # # # # #

if (inclcrit == 1) {overlap <- overlap1
criteria <- "KSADS + rs-fMRI recommended use"
} else if (inclcrit == 2) {overlap <- overlap2
criteria <- "CBCL + rs-fMRI recommended use"
} else if (inclcrit == 3) {overlap <- overlap3
criteria <- "KSADS + CBCL + rs-fMRI recommended use"
}

setwd("/Users/adamkaminski/Desktop/stimproj/data/nda_downloads/")
write.csv(overlap,paste("subs_inclcrit",inclcrit,".csv",sep=""),row.names = FALSE)

```

#### FC data (step 1)
##### From NDADownloadManager
##### Keep caudate, putamen, and nucleus accumbens columns only
##### Remove rows of individuals who do not meet selected criteria
##### Convert long (by timepoint) to wide and calculate rs-fMRI differences between baseline and year 2 timepoint
##### Remove "none" network
##### Remove individuals missing caudate, putamen, and nucleus accumbens - cortical network FC data
```{r, warning=FALSE}
setwd("/Users/adamkaminski/Desktop/stimproj/data/")
netdat <- read.csv('mrirscor02_v1.csv')
keep <- 1:dim(netdat)[2]

# Keep only caudate, putamen, and nucleus accumbens columns
for (i in 13:length(netdat)){
  if (isFALSE(grepl("cde",colnames(netdat)[i],fixed=TRUE)) & 
      isFALSE(grepl("pt",colnames(netdat)[i],fixed=TRUE)) &
      isFALSE(grepl("aa",colnames(netdat)[i],fixed=TRUE))) {
    keep[i] <- 0
  }
}
netdat <- netdat[,c(keep)]

# Keep only included subs
netdat <- netdat[netdat$src_subject_id%in%overlap,]

# Convert long to wide
netdat$eventname[netdat$eventname=="baseline_year_1_arm_1"] <- 0
netdat$eventname[netdat$eventname=="2_year_follow_up_y_arm_1"] <- 2
netdat <- reshape(netdat, idvar = "src_subject_id", timevar = "eventname", direction = "wide")

# Remove "none" network
netdat <- netdat[,-((1:dim(netdat)[2])*as.numeric(grepl("_none_",colnames(netdat),fixed=TRUE)))]

# # # # # # # # # # # # # # # # # # # # # # #
# !!! Below depends on user input above !!! #
# # # # # # # # # # # # # # # # # # # # # # #

# Combine networks if desired
if (combine == 1) {
  CON <- as.data.frame(netdat[,grepl("_cerc_",colnames(netdat),fixed=TRUE)])
  SAL <- as.data.frame(netdat[,grepl("_sa_",colnames(netdat),fixed=TRUE)])
  SMH <- netdat[,grepl("_smh_",colnames(netdat),fixed=TRUE)]
  SMM <- netdat[,grepl("_smm_",colnames(netdat),fixed=TRUE)]
  
  avgconsal <- matrix(0,dim(netdat)[1],dim(CON)[2])
  avgsmhsmm <- matrix(0,dim(netdat)[1],dim(SMH)[2])
  for (i in 1:dim(CON)[2]) {
    avgconsal[,i] <- (as.numeric(CON[,i]) + as.numeric(SAL[,i]))/2
    avgsmhsmm[,i] <- (as.numeric(SMH[,i]) + as.numeric(SMM[,i]))/2
  }
  colnames(avgconsal) <-  gsub('_cerc_','_cercsa_',colnames(CON))
  colnames(avgsmhsmm) <- gsub('_smh_','_smhsmm_',colnames(SMH))
  
  netdat <- netdat[,!grepl("_cerc_",colnames(netdat),fixed=TRUE)]
  netdat <- netdat[,!grepl("_sa_",colnames(netdat),fixed=TRUE)]
  netdat <- netdat[,!grepl("_smh_",colnames(netdat),fixed=TRUE)]
  netdat <- netdat[,!grepl("_smm_",colnames(netdat),fixed=TRUE)]

  netdat <- cbind(netdat,avgconsal)
  netdat <- cbind(netdat,avgsmhsmm)
}

if (combine == 1) {
  net_codes <- c("_au_","_cercsa_","_copa_","_df_","_dsa_","_fopa_","_rst_",
                 "_smhsmm_","_vta_","vs")
} else {
  net_codes <- c("_au_","_cerc_","_copa_","_df_","_dsa_","_fopa_","_rst_",
                 "_sa_","_smh_","_smm_","_vta_","_vs_")
}

# Create difference scores
# Determine number of seed-network FC connections:
#   - 10 functional networks (removed "none" network; combining cerc and sa, and smh and smm networks)
#   - 6 striatal seed
#   - 10 x 6 = 60

if (combine == 1) {n<-(10*6)} else {n<-(12*6)}

diff <- as.data.frame(matrix(0,dim(netdat)[1],n))
count <- 1
for (i in 1:length(net_codes)) {
  temp_net <- netdat[,grepl(net_codes[i],colnames(netdat),fixed=TRUE)]
  for (se in 1:6) {
    str1 <- colnames(temp_net)[se]
    str2 <- colnames(temp_net)[se+6]
    len <- nchar(str1)
    if (substr(str1,1,len-2) == substr(str2,1,len-2)) {
      new_str <- gsub('rsfmri_cor_ngd_','',substr(str1,1,len-2))
      new_str <- gsub('_scs','',new_str)
      colnames(diff)[count] <- new_str
      diff[,count] <- as.numeric(temp_net[,se]) - as.numeric(temp_net[,se+6])
      count <- count + 1
    } else {
      stop(paste("These colnames do not match:",se,"and",se+6))
    }
  }
}

# remove unnecessary cols (i.e., 0 + 2 FC) from netdat and add change in FC
if (combine == 1) {netdat <- netdat[,c(1:11,60:69)]
} else {netdat <- netdat[,c(1:11,84:93)]}

netdat <- cbind(netdat,diff)

# remove subjects with MISSING FC DATA
netdat <- netdat[complete.cases(netdat), ]

new_overlap <- netdat$src_subject_id

writeLines(paste("Using ",criteria," criteria (n=",length(overlap),")\nOf these, ",dim(netdat)[1]," people have required FC data",sep=""))

# trim site IDs 
netdat$rsfmri_cor_ngd_scs_visitid.0 <- substr(netdat$rsfmri_cor_ngd_scs_visitid.0,1,4)
netdat$rsfmri_cor_ngd_scs_visitid.2 <- substr(netdat$rsfmri_cor_ngd_scs_visitid.2,1,4)

# create a age difference variable
netdat$age_diff <- as.numeric(netdat$interview_age.2) - as.numeric(netdat$interview_age.0)

# create 0 and 1 sex variable
netdat$sex <- netdat$sex.0
netdat$sex[netdat$sex=="M"] <- 1
netdat$sex[netdat$sex=="F"] <- 0

#
# add education variables
#
setwd("/Users/adamkaminski/Desktop/stimproj/data/nda_downloads/")
demos <- read.csv("demographics.csv",header=TRUE)
# Keep only included subs
demos <- demos[demos$src_subject_id%in%new_overlap,]
# get z-scores
demos$parent_ed_z <- (demos$parent_ed-mean(demos$parent_ed,na.rm=TRUE))/sd(demos$parent_ed,na.rm=TRUE)
demos$partner_ed_z <- (demos$partner_ed-mean(demos$partner_ed,na.rm=TRUE))/sd(demos$partner_ed,na.rm=TRUE) 
demos$comb_inc[demos$comb_inc==999] <- NA
demos$comb_inc[demos$comb_inc==777] <- NA
demos$comb_inc_z <- (demos$comb_inc-mean(demos$comb_inc,na.rm=TRUE))/sd(demos$comb_inc,na.rm=TRUE)
# add ses variable
for (i in 1:length(demos$parent_ed_z)) {
  if (is.na(demos$partner_ed_z[i])) {
    if (is.na(demos$comb_inc_z[i])) {
      demos$ses[i] <- demos$parent_ed_z[i]
    } else {
      demos$ses[i] <- (demos$parent_ed_z[i] + demos$comb_inc_z[i])/2
    }
  } else if (is.na(demos$comb_inc_z[i])) {
      demos$ses[i] <- (demos$parent_ed_z[i] + demos$partner_ed_z[i])/2
  } else {
    demos$ses[i] <- (demos$parent_ed_z[i] + demos$partner_ed_z[i] + demos$comb_inc_z[i])/3
  }
}

# match IDs
demos <- demos[order(demos$src_subject_id),]
netdat <- netdat[order(netdat$src_subject_id),]
if (sum(as.numeric(demos$src_subject_id==netdat$src_subject_id))==dim(demos)[1]) {
  netdat <- cbind(netdat,demos$ses)
}
colnames(netdat)[dim(netdat)[2]] <- "ses"

#require(knitr)
writeLines("First 20 rows of wide dataframe:")
kable(netdat[1:20,])

setwd("/Users/adamkaminski/Desktop/stimproj/data/FC_data/")
if (combine == 1) {write.csv(netdat,'mrirscor02_v2_combine_1.csv')
} else {write.csv(netdat,'mrirscor02_v2_combine_0.csv')}

```

#### FC data (step 2)
##### Convert wide to long (by network); each network has its own row for each individual (1 column per striatal seed)
```{r,warning=FALSE}

# make netdat long by network:
if (combine == 1) { networks <- c("auditory","cingulo.op.salience","cingulo.parietal",
              "default","dorsal","fronto","retrosplenial",
              "sensorimotor","ventral","visual")
} else { networks <- c("auditory","cingulo.opercular","cingulo.parietal",
              "default","dorsal","fronto","retrosplenial","salience",
              "sensorimotor.hand","sensorimotor.mouth",
              "ventral","visual")
}

seeds <- c("cdelh","ptlh","aalh",
           "cderh","ptrh","aarh")

temp <- as.data.frame(matrix(0,dim(netdat)[1]*length(networks),length(seeds)+10))
start <- 1
hit <- 1
inc <- length(new_overlap) - 1
for (i in 1:length(seeds)) {
  for (col in 1:length(netdat)) {
    if (grepl(seeds[i],colnames(netdat)[col],fixed=TRUE)) {
      temp[start:c(start+inc),i+11] <- netdat[,col]
      temp[start:c(start+inc),1+10] <- netdat$sex
      temp[start:c(start+inc),1+9] <- netdat$age_diff
      temp[start:c(start+inc),1+8] <- netdat$ses
      temp[start:c(start+inc),1+7] <- netdat$rsfmri_cor_ngd_scs_visitid.2
      temp[start:c(start+inc),1+6] <- netdat$rsfmri_cor_ngd_scs_visitid.0
      temp[start:c(start+inc),1+5] <- netdat$rsfmri_cor_ngd_scs_stnvols.2 # num vols < 0.2 mm FD
      temp[start:c(start+inc),1+4] <- netdat$rsfmri_cor_ngd_scs_stnvols.0 # num vols < 0.2 mm FD
      temp[start:c(start+inc),1+3] <- netdat$rsfmri_cor_ngd_scs_meanmn.2 # mean mm FD
      temp[start:c(start+inc),1+2] <- netdat$rsfmri_cor_ngd_scs_meanmn.0 # mean mm FD
      temp[start:c(start+inc),1+1] <- networks[hit]
      temp[start:c(start+inc),1] <- netdat$src_subject_id
      start <- start + inc + 1
      hit <- hit + 1
    }
  }
  start <- 1
  hit <- 1
}
colnames(temp)[1:11] <- c("ID","network","meanFD.0","meanFD.2","FD.under.0.2.0","FD.under.0.2.2",
                         "site.0","site.2","ses","age.diff","sex")
colnames(temp)[12:17] <- c("left.caudate","left.putamen","left.accumbens",
                          "right.caudate","right.putamen","right.accumbens")

temp <- temp[order(temp$network),]
temp <- temp[order(temp$ID),]

writeLines("First 20 rows of long dataframe:")
kable(temp[1:20,])

setwd("/Users/adamkaminski/Desktop/stimproj/data/FC_data/")
if (combine == 1) { write.csv(temp,'mrirscor02_v3_combine_1.csv') 
} else { write.csv(temp,'mrirscor02_v3_combine_0.csv')}

netdat_l <- temp

```

#### Medication data
##### Remove rows of individuals who do not meet selected criteria
##### Save csv, decode drug codes by hand using website: https://bioportal.bioontology.org/
```{r, warning=FALSE}

# This chunk takes the original medication spreadsheet (from NDADownloadManager; in long format) and excludes all individuals who do not meet the above criteria (i.e., KSADS + rs-fMRI). Therefore, the output will have row numbers corresponding to: (314 subjects * 3 timepoints) - the number of missing timepoint data. This is what I then give to Brylee to decode the drug information using this website: https://bioportal.bioontology.org/

setwd("/Users/adamkaminski/Desktop/stimproj/data/")
med <- read.csv('medsy01.csv')

med_subs <- med[med$The.NDAR.Global.Unique.Identifier..GUID..for.research.subject%in%new_overlap,]
temp <- reshape(med_subs, idvar = "The.NDAR.Global.Unique.Identifier..GUID..for.research.subject", timevar = "The.event.name.for.which.the.data.was.collected", direction = "wide")
a <- sort(temp$The.NDAR.Global.Unique.Identifier..GUID..for.research.subject)
b <- sort(new_overlap)
if (sum(as.numeric(a==b)) != length(b)) {
  stop("IDs for med data don't match IDs which are meeting criteria on KSADS + rs-fMRI. Something is wrong!")
}

setwd("/Users/adamkaminski/Desktop/stimproj/data/ABCD_data/")
write.csv(med_subs,"medsy01_inclIDs.csv",na = "",row.names = FALSE)

```

#### Decoded medication data
```{r, warning = FALSE}

# Import and combine data, match to true subs, convert long to wide

setwd("/Users/adamkaminski/Desktop/stimproj/data/")
subs1 <- read.csv(file = './subIDs_first.csv', header=TRUE)
subs2 <- read.csv(file = './subIDs_second.csv', header=TRUE)
cnames <- colnames(subs1)
colnames(subs2) <- cnames
subs1_2 <- rbind(subs1,subs2)

subs <- subs1_2[subs1_2$subID%in%new_overlap,]

stimsubs <- reshape(subs, idvar = "subID", timevar = "time", direction = "wide")

```

#### "getgroups" function
```{r}

# get_groups function
# input: reshaped df with drug info (1 row per individual) and search term for column
# output: df with two columns (one for ID and another for drug group)

get_groups <- function(df,search) {
  numrows <- nrow(df)
  stimgroups = as.data.frame(matrix('none',numrows,2))
  colnames(stimgroups) <- c("subID","group")
  stimgroups$subID <- df$subID
  
  stimgroupcount <- as.data.frame(matrix(0,1,9))

  df <- df[,grepl(search,colnames(stimsubs))]
  df$ID <- stimsubs$subID
  
  for (i in 1:dim(df)[1]) {
    if (is.na(df[i,1])  || is.na(df[i,2]) || is.na(df[i,3])) {
      stimgroups$group[i] <- 'missing'
      stimgroupcount[1,8] <- stimgroupcount[1,8] + 1
    } else {
      #   stim 0 only (0)
      if (df[i,1] == 1  && df[i,2] == 0 && df[i,3] == 0) {
        stimgroups$group[i] <- 'b'
        stimgroupcount[1,1] <- stimgroupcount[1,1] + 1
      }
      #   stim 1 only (1)
      else if (df[i,1] == 0  && df[i,2] == 1 && df[i,3] == 0) {
        stimgroups$group[i] <- 'y1'
        stimgroupcount[1,2] <- stimgroupcount[1,2] + 1
      }
      #   stim 2 only (2)
      else if (df[i,1] == 0  && df[i,2] == 0 && df[i,3] == 1) {
        stimgroups$group[i] <- 'y2'
        stimgroupcount[1,3] <- stimgroupcount[1,3] + 1
      }
      #   stim 0 + 1 (3)
      else if (df[i,1] == 1  && df[i,2] == 1 && df[i,3] == 0) {
        stimgroups$group[i] <- 'b+y1'
        stimgroupcount[1,4] <- stimgroupcount[1,4] + 1
      }
      #   stim 0 + 2 (4)
      else if (df[i,1] == 1  && df[i,2] == 0 && df[i,3] == 1) {
        stimgroups$group[i] <- 'b+y2'
        stimgroupcount[1,5] <- stimgroupcount[1,5] + 1
      }
      #   stim 1 + 2 (5)
      else if (df[i,1] == 0  && df[i,2] == 1 && df[i,3] == 1) {
        stimgroups$group[i] <- 'y1+y2'
        stimgroupcount[1,6] <- stimgroupcount[1,6] + 1
      }
      #   stim 0 + 1 + 2 (6)
      else if (df[i,1] == 1  && df[i,2] == 1 && df[i,3] == 1) {
        stimgroups$group[i] <- 'b+y1+y2'
        stimgroupcount[1,7] <- stimgroupcount[1,7] + 1
      }
      # no stim
      else {
        stimgroupcount[1,9] <- stimgroupcount[1,9] + 1
      }
    }
  }
  
  missing <- df[stimgroups$group=='missing',]
  missing <- missing[is.na(missing[,2]),]
  
  print(paste(search,": ",dim(missing)[1]," individuals are missing y1 data",sep=""))
  
  for (i in 1:dim(missing)[1]) {
    if (missing[i,1] == 1 && missing[i,3] == 1) {
      stimgroups$group[stimgroups$subID==missing$ID[i]] <- 'b+y2'
    } 
    else if (missing[i,1] == 0 && missing[i,3] == 1) {
      stimgroups$group[stimgroups$subID==missing$ID[i]] <- 'y2'
    } 
    else if (missing[i,1] == 1 && missing[i,3] == 0) {
      stimgroups$group[stimgroups$subID==missing$ID[i]] <- 'b'
    } 
    else if (missing[i,1] == 0 && missing[i,3] == 0) {
      stimgroups$group[stimgroups$subID==missing$ID[i]] <- 'none'
    } 
  }
  
return(stimgroups)
} 

```

#### Create groups based on reported psychotropic medications (6 categories)
##### Report missing data
##### Medication data
```{r,warning=FALSE,message=FALSE}

# function "get_groups" defined in hidden chunk
# input: reshaped df with drug info (1 row per individual)
# output: df with two columns (one for ID and another for drug group)

setwd("/Users/adamkaminski/Desktop/stimproj/data/models/6.2/")
#load("env15.RData")

labels <- c("ADHD_stim","ADHD_non.stim","Anti.depressant",
            "seizures_and_bipolar_disorder","antihypertensive",
            "antipsychotic")

tab <- matrix(0,length(labels),8)
colnames(tab) <- c("b","b+y1","b+y1+y2","b+y2","none","y1","y1+y2","y2")
rownames(tab) <-c("ADHD Stimulant","ADHD Non-stimulant","Antidepressant",
            "Seizures and Bipolar Disorder","Antihypertensive",
            "Antipsychotic")

for (lab in 1:length(labels)) {
  
  stimgroups <- get_groups(stimsubs,labels[lab])
  stimgroups <- stimgroups[stimgroups$subID%in%netdat1_gm$src_subject_id,]
  temp <- table(stimgroups$group)
  tab[lab,colnames(tab)%in%names(temp)] <- temp

}

tab <- as.data.frame(tab[, c(1,6,8,2,4,7,3,5)])
tab[,9] <- tab$none
colnames(tab)[8:9] <- c("any","none")
for (i in 1:6) { tab[i,8] <- sum(tab[i,1:7]) }

tab2 <- matrix(0,6,5)
tab2[1,1] <- sum(tab[1,1:3])
tab2[2,1] <- sum(tab[2,1:3])
tab2[3,1] <- sum(tab[3,1:3])
tab2[4,1] <- sum(tab[4,1:3])
tab2[5,1] <- sum(tab[5,1:3])
tab2[6,1] <- sum(tab[6,1:3])
tab2[1,2] <- sum(tab[1,4:6])
tab2[2,2] <- sum(tab[2,4:6])
tab2[3,2] <- sum(tab[3,4:6])
tab2[4,2] <- sum(tab[4,4:6])
tab2[5,2] <- sum(tab[5,4:6])
tab2[6,2] <- sum(tab[6,4:6])
tab2[1:6,3] <- tab[1:6,7]
tab2[1:6,4] <- tab[1:6,8]
tab2[1:6,5] <- tab[1:6,9]

colnames(tab2) <- c("1","2","3","Any","None")
rownames(tab2) <- rownames(tab)

```

```{r}

# Resources
# - https://gt.albert-rapp.de/styling.html
# - https://gt.rstudio.com/reference/tab_footnote.html
require(gt)
nice_tab <- gt(as.data.frame(tab),
   rownames_to_stub = TRUE) |>
   cols_label(
     'b'=md("**B**"),'y1'=md("**Y1**"),'y2'=md("**Y2**"),'b+y1'=md("**B+Y1**"),
     'b+y2'=md("**B+Y2**"),'y1+y2'=md("**Y1+Y2**"),'b+y1+y2'=md("**B+Y1+Y2**"),
     'any'=md("**Any**"),'none'=md("**None**")
   ) |>
   tab_header(
    title = 'Reported Psychotropic Medications',
    subtitle = paste("At what timepoints individuals (total n = ",tab[1,8]+tab[1,9],") reported a psychotropic medication prescription",sep="")
    ) |> 
  opt_stylize(style = 3, color = 'gray') |> 
  tab_options(
    # These were the ones we applied in the first chapter
    data_row.padding = px(2),
    summary_row.padding = px(3), # A bit more padding for summaries
    row_group.padding = px(4)    # And even more for our groups
    ) |> 
  tab_source_note(
    source_note = "B = baseline timepoint; Y1 = year 1 timepoint; Y2 = year 2 timepoint;
    All columns, besides Any and None, indicate only those timepoints and no other timepoints"
    )
  
nice_tab

```

#### Combine psychotropic drug data and FC data
```{r,warning=FALSE,include=FALSE}

# Get psychotropic drug groups
stimgroups <- get_groups(stimsubs,"ADHD_stim")
nonstimadhdgroups <- get_groups(stimsubs,"ADHD_non.stim")
antidepgroups <- get_groups(stimsubs,"Anti.depressant")
bpdgroups <- get_groups(stimsubs,"seizures_and_bipolar_disorder")
ahtgroups <- get_groups(stimsubs,"antihypertensive")
antipsygroups <- get_groups(stimsubs,"antipsychotic")

# Combine psychotropic drug groups
allgroups <- cbind(stimgroups,nonstimadhdgroups$group,antidepgroups$group,
                   bpdgroups$group,ahtgroups$group,antipsygroups$group)
colnames(allgroups) <- c("subID","ADHD_stim","ADHD_non.stim","Anti.depressant",
                         "seizures_and_bipolar_disorder","antihypertensive","antipsychotic")

# Replace all drug categories with exposed or not (does not depend on number of timepoints reported)
allgroups[allgroups=="none"] <- 0
allgroups[allgroups!=0] <- 1

allgroups$subID <- stimgroups$subID

# Create variable for length of time on a stimulant (reported at 0, 1, 2, or 3 timepoints)
stimgroups$length[stimgroups$group=="none"] <- 0
stimgroups$length[stimgroups$group=="b"] <- 1
stimgroups$length[stimgroups$group=="y1"] <- 1
stimgroups$length[stimgroups$group=="y2"] <- 1
stimgroups$length[stimgroups$group=="b+y1"] <- 2
stimgroups$length[stimgroups$group=="b+y2"] <- 2
stimgroups$length[stimgroups$group=="y1+y2"] <- 2
stimgroups$length[stimgroups$group=="b+y1+y2"] <- 3

# combine group info with FC df
# 12 is the number of networks
# wide:
netdat <- netdat[order(netdat$src_subject_id),]
stimgroups <- stimgroups[order(stimgroups$subID),]
allgroups <- allgroups[order(allgroups$subID),]
if (sum(as.numeric(netdat$src_subject_id == stimgroups$subID))==dim(netdat)[1]) {
  netdat$stim_group_lab <- stimgroups$group
  netdat$stim_length <- stimgroups$length
}  else {
  stop(paste("IDs do not match"))
}
if (sum(as.numeric(netdat$src_subject_id == allgroups$subID))==dim(netdat)[1]) {
  # Stim or no?
  netdat$stim_group_bi <- allgroups$ADHD_stim 
  # Other non-stim med or no? 
  netdat$nonstim_med_bi <- as.character(as.numeric((allgroups$ADHD_non.stim == "1" | allgroups$Anti.depressant == "1" | allgroups$seizures_and_bipolar_disorder == "1" | allgroups$antihypertensive == "1" | allgroups$antipsychotic == "1"))) 
} else {
  stop(paste("IDs do not match"))
}

# long:
start <- 1
netdat_l <- netdat_l[order(netdat_l$ID),]
netdat_l <- netdat_l[order(netdat_l$network),]
temp <- table(netdat_l$network)
numnet <- length(temp)
for (i in 1:numnet) {
  netdat_l$stim_bi[start:c(start+(temp[i]-1))] <- netdat$stim_group_bi
  netdat_l$nonstim_med_bi[start:c(start+(temp[i]-1))] <- netdat$nonstim_med_bi
  netdat_l$stimlen[start:c(start+(temp[i]-1))] <- netdat$stim_length
  start <- start + temp[i]
}

# troubleshoot issues here:
netdat_l[,c(3:6,9,11:16)] <- as.numeric(unlist(netdat_l[,c(3:6,9,11:16)]))

colnames(netdat)[c(8,11,14,18,21)] <- c("FD.under.0.2.2","meanFD.2","site.0",
                                        "FD.under.0.2.0","meanFD.0")

netdat[,c(8,11,18,21)] <- as.numeric(unlist(netdat[,c(8,11,18,21)]))

```

### Create dfs for different medication comparisons
```{r,warning=FALSE}

# Stim + possibly other vs. NO stim (but possibly other meds; PLUS none)
# DV is stim_group_bi
netdat1 <- netdat 
# Stim ONLY vs. no meds AT ALL
# DV is stim_group_bi
netdat2 <- netdat[netdat$nonstim_med_bi!=1,]
# ALL other meds (excluding stim) vs. no meds AT ALL
# DV is nonstim_med_bi
netdat3 <- netdat[netdat$stim_group_bi!=1,]

# long data:

# Stim + polypharmacy vs. NO stims (but possibly other meds; PLUS none)
# DV is stim_group_bi
netdat1_l <- netdat_l
# Stim ONLY vs. no meds AT ALL
# DV is stim_group_bi
netdat2_l <- netdat_l[netdat_l$nonstim_med_bi!=1,]
# ALL other meds (excluding stim) vs. no meds AT ALL
# DV is nonstim_med_bi
netdat3_l <- netdat_l[netdat_l$stim_bi!=1,]

```

### n for each group
```{r,warning=FALSE,message=FALSE}
require(brms)
require(bayesplot)
require(ggplot2)
require(forcats)

setwd("/Users/adamkaminski/Desktop/stimproj/data/models/6.2/")
load("env15.RData")

df_tab <- as.data.frame(matrix(0,3,2))
df_tab[1,1] <- table(netdat1$stim_group_bi)[2]
df_tab[2,1] <- table(netdat2$stim_group_bi)[2]
df_tab[3,1] <- table(netdat3$nonstim_med_bi)[2]
df_tab[1,2] <- table(netdat1$stim_group_bi)[1]
df_tab[2,2] <- table(netdat2$stim_group_bi)[1]
df_tab[3,2] <- table(netdat3$nonstim_med_bi)[1]

colnames(df_tab) <- c("Medication","Naive")
rownames(df_tab) <- c("Nonexclusive Stimulant vs. Possible Other Medication","Exclusive Stimulant vs. No Medication",
                      "Definite Other Medication vs. No Medication")

# Plot 
gt(df_tab,
   rownames_to_stub = TRUE) |>
  opt_stylize(style = 3, color = 'gray'
    )

```

### MOTION check 1: Differences between each set of groups 
```{r,warning=FALSE,message=FALSE}

motion_tab <- matrix(0,12,4)

motion_vars_1 <- netdat1[,c(18,21,8,11,87)]
motion_vars_2 <- netdat2[,c(18,21,8,11,87)]
motion_vars_3 <- netdat3[,c(18,21,8,11,88)]

row <- 1
col <- 1
for (i in 1:12) {
  if (i < 5) {
    t_out <- t.test(motion_vars_1[,col]~netdat1$stim_group_bi)
    col <- col + 1
    if (col == 5) { col <- 1 }
  } else if (i < 9) {
    t_out <- t.test(motion_vars_2[,col]~netdat2$stim_group_bi)
    col <- col + 1
    if (col == 5) { col <- 1 }
  } else if (i < 13) {
    t_out <- t.test(motion_vars_3[,col]~netdat3$nonstim_med_bi)
    col <- col + 1
    if (col == 5) { col <- 1 }
  }
    motion_tab[row,1] <- round(t_out$estimate[2],digits=3)
    motion_tab[row,2] <- round(t_out$estimate[1],digits=3)
    motion_tab[row,3] <- round(t_out$statistic,digits=3)
    motion_tab[row,4] <- round(t_out$p.value,digits=3)
    row <- row + 1
}

colnames(motion_tab) <- c("Medication Group","Naive Group","t statistic","p value")
rownames(motion_tab) <- c("Baseline Length (sec)","Baseline Mean FD (mm)","Year 2 Length (sec)","Year 2 Mean FD (mm)","Baseline Length (sec)","Baseline Mean FD (mm)","Year 2 Length (sec)","Year 2 Mean FD (mm)","Baseline Length (sec)","Baseline Mean FD (mm)","Year 2 Length (sec)","Year 2 Mean FD (mm)")

gt(as.data.frame(motion_tab),
   rownames_to_stub = TRUE) |>
   tab_header(
    title = 'Group rs-FC Motion Differences') |> 
  opt_stylize(style = 6, color = 'gray') |> 
      tab_row_group(
    label = "Other Med, Nothing",
    rows = 9:12
  ) |> 
    tab_row_group(
    label = "Exc. Stimulant, Nothing",
    rows = 5:8
  ) |> 
    tab_row_group(
    label = "Stimulant, No Stimulant",
    rows = 1:4
  )

```

### MOTION check 2: Differences in each group between time-points
```{r,warning=FALSE,message=FALSE}

motion_vars_1_long <- reshape(motion_vars_1, 
        direction = "long",
        varying = list(names(motion_vars_1)[c(1,3)],names(motion_vars_1)[c(2,4)]),
        v.names = c("Length_sec","MeanFD_mm"),
        timevar = "Time")

motion_vars_2_long <- reshape(motion_vars_2, 
        direction = "long",
        varying = list(names(motion_vars_2)[c(1,3)],names(motion_vars_2)[c(2,4)]),
        v.names = c("Length_sec","MeanFD_mm"),
        timevar = "Time")

motion_vars_3_long <- reshape(motion_vars_3, 
        direction = "long",
        varying = list(names(motion_vars_3)[c(1,3)],names(motion_vars_3)[c(2,4)]),
        v.names = c("Length_sec","MeanFD_mm"),
        timevar = "Time")

require("ggpubr")

cat("GROUPS = Stimulant, No Stimulant\nTIME = Baseline, Year 2\nDV = Length (sec)")
print(summary(aov(Length_sec ~ Time*stim_group_bi + Error(factor(id)/Time), data = motion_vars_1_long)))
ggboxplot(motion_vars_1_long, x = "Time", y = "Length_sec", color = "stim_group_bi",
          palette = c("#00AFBB", "#E7B800"))

cat("GROUPS = Stimulant, No Stimulant\nTIME = Baseline, Year 2\nDV = Mean FD (mm)")
print(summary(aov(MeanFD_mm ~ Time*stim_group_bi + Error(factor(id)/Time), data = motion_vars_1_long)))
ggboxplot(motion_vars_1_long, x = "Time", y = "MeanFD_mm", color = "stim_group_bi",
          palette = c("#00AFBB", "#E7B800"))

cat("GROUPS = Exc. Stimulant, Nothing\nTIME = Baseline, Year 2\nDV = Length (sec)")
print(summary(aov(Length_sec ~ Time*stim_group_bi + Error(factor(id)/Time), data = motion_vars_2_long)))
ggboxplot(motion_vars_2_long, x = "Time", y = "Length_sec", color = "stim_group_bi",
          palette = c("#00AFBB", "#E7B800"))

cat("GROUPS = Exc. Stimulant, Nothing\nTIME = Baseline, Year 2\nDV = Mean FD (mm)")
print(summary(aov(MeanFD_mm ~ Time*stim_group_bi + Error(factor(id)/Time), data = motion_vars_2_long)))
ggboxplot(motion_vars_2_long, x = "Time", y = "MeanFD_mm", color = "stim_group_bi",
          palette = c("#00AFBB", "#E7B800"))

cat("GROUPS = Other Med., Nothing\nTIME = Baseline, Year 2\nDV = Length (sec)")
print(summary(aov(Length_sec ~ Time*nonstim_med_bi + Error(factor(id)/Time), data = motion_vars_3_long)))
ggboxplot(motion_vars_3_long, x = "Time", y = "Length_sec", color = "nonstim_med_bi",
          palette = c("#00AFBB", "#E7B800"))

cat("GROUPS = Other Med., Nothing\nTIME = Baseline, Year 2\nDV = Mean FD (mm)")
print(summary(aov(MeanFD_mm ~ Time*nonstim_med_bi + Error(factor(id)/Time), data = motion_vars_3_long)))
ggboxplot(motion_vars_3_long, x = "Time", y = "MeanFD_mm", color = "nonstim_med_bi",
          palette = c("#00AFBB", "#E7B800"))


```

### MOTION check 3: Excluding mean FD >= 0.5mm
```{r,warning=FALSE,message=FALSE}

netdat1_gm <- netdat1[netdat1$meanFD.0<0.5&netdat1$meanFD.2<0.5,]
netdat2_gm <- netdat2[netdat2$meanFD.0<0.5&netdat2$meanFD.2<0.5,]
netdat3_gm <- netdat3[netdat3$meanFD.0<0.5&netdat3$meanFD.2<0.5,]

df_tab <- as.data.frame(matrix(0,3,2))
df_tab[1,1] <- table(netdat1_gm$stim_group_bi)[2]
df_tab[2,1] <- table(netdat2_gm$stim_group_bi)[2]
df_tab[3,1] <- table(netdat3_gm$nonstim_med_bi)[2]
df_tab[1,2] <- table(netdat1_gm$stim_group_bi)[1]
df_tab[2,2] <- table(netdat2_gm$stim_group_bi)[1]
df_tab[3,2] <- table(netdat3_gm$nonstim_med_bi)[1]

colnames(df_tab) <- c("Medication","Naive")
rownames(df_tab) <- c("Nonexclusive Stimulant vs. Possible Other Medication","Exclusive Stimulant vs. No Medication","Definite Other Medication vs. No Medication")

# Plot 
gt(df_tab,
   rownames_to_stub = TRUE) |>
  tab_header(
    title = 'Group sizes, Excluding meanFD>0.5mm') |> 
  opt_stylize(style = 3, color = 'pink'
    )

motion_tab <- matrix(0,12,4)

motion_vars_1 <- netdat1_gm[,c(18,21,8,11,87)]
motion_vars_2 <- netdat2_gm[,c(18,21,8,11,87)]
motion_vars_3 <- netdat3_gm[,c(18,21,8,11,88)]

row <- 1
col <- 1
for (i in 1:12) {
  if (i < 5) {
    t_out <- t.test(motion_vars_1[,col]~netdat1_gm$stim_group_bi)
    col <- col + 1
    if (col == 5) { col <- 1 }
  } else if (i < 9) {
    t_out <- t.test(motion_vars_2[,col]~netdat2_gm$stim_group_bi)
    col <- col + 1
    if (col == 5) { col <- 1 }
  } else if (i < 13) {
    t_out <- t.test(motion_vars_3[,col]~netdat3_gm$nonstim_med_bi)
    col <- col + 1
    if (col == 5) { col <- 1 }
  }
    motion_tab[row,1] <- round(t_out$estimate[2],digits=3)
    motion_tab[row,2] <- round(t_out$estimate[1],digits=3)
    motion_tab[row,3] <- round(t_out$statistic,digits=3)
    motion_tab[row,4] <- round(t_out$p.value,digits=3)
    row <- row + 1
}

colnames(motion_tab) <- c("Medication Group","Naive Group","t statistic","p value")
rownames(motion_tab) <- c("Baseline Length (sec)","Baseline Mean FD (mm)","Year 2 Length (sec)","Year 2 Mean FD (mm)","Baseline Length (sec)","Baseline Mean FD (mm)","Year 2 Length (sec)","Year 2 Mean FD (mm)","Baseline Length (sec)","Baseline Mean FD (mm)","Year 2 Length (sec)","Year 2 Mean FD (mm)")

gt(as.data.frame(motion_tab),
   rownames_to_stub = TRUE) |>
   tab_header(
    title = 'Group rs-FC Motion Differences, Excluding meanFD>0.5mm') |> 
  opt_stylize(style = 6, color = 'pink') |> 
      tab_row_group(
    label = "Other Med, Nothing",
    rows = 9:12
  ) |> 
    tab_row_group(
    label = "Exc. Stimulant, Nothing",
    rows = 5:8
  ) |> 
    tab_row_group(
    label = "Stimulant, No Stimulant",
    rows = 1:4
  )

#
# Testing for Time X Group differences for motion parameters
#

motion_vars_1_long <- reshape(motion_vars_1, 
        direction = "long",
        varying = list(names(motion_vars_1)[c(1,3)],names(motion_vars_1)[c(2,4)]),
        v.names = c("Length_sec","MeanFD_mm"),
        timevar = "Time")

motion_vars_2_long <- reshape(motion_vars_2, 
        direction = "long",
        varying = list(names(motion_vars_2)[c(1,3)],names(motion_vars_2)[c(2,4)]),
        v.names = c("Length_sec","MeanFD_mm"),
        timevar = "Time")

motion_vars_3_long <- reshape(motion_vars_3, 
        direction = "long",
        varying = list(names(motion_vars_3)[c(1,3)],names(motion_vars_3)[c(2,4)]),
        v.names = c("Length_sec","MeanFD_mm"),
        timevar = "Time")

cat("GROUPS = Stimulant, No Stimulant\nTIME = Baseline, Year 2\nDV = Length (sec)")
print(summary(aov(Length_sec ~ Time*stim_group_bi + Error(factor(id)/Time), data = motion_vars_1_long)))
ggboxplot(motion_vars_1_long, x = "Time", y = "Length_sec", color = "stim_group_bi",
          palette = c("#00AFBB", "#E7B800"))

cat("GROUPS = Stimulant, No Stimulant\nTIME = Baseline, Year 2\nDV = Mean FD (mm)")
print(summary(aov(MeanFD_mm ~ Time*stim_group_bi + Error(factor(id)/Time), data = motion_vars_1_long)))
ggboxplot(motion_vars_1_long, x = "Time", y = "MeanFD_mm", color = "stim_group_bi",
          palette = c("#00AFBB", "#E7B800"))

cat("GROUPS = Exc. Stimulant, Nothing\nTIME = Baseline, Year 2\nDV = Length (sec)")
print(summary(aov(Length_sec ~ Time*stim_group_bi + Error(factor(id)/Time), data = motion_vars_2_long)))
ggboxplot(motion_vars_2_long, x = "Time", y = "Length_sec", color = "stim_group_bi",
          palette = c("#00AFBB", "#E7B800"))

cat("GROUPS = Exc. Stimulant, Nothing\nTIME = Baseline, Year 2\nDV = Mean FD (mm)")
print(summary(aov(MeanFD_mm ~ Time*stim_group_bi + Error(factor(id)/Time), data = motion_vars_2_long)))
ggboxplot(motion_vars_2_long, x = "Time", y = "MeanFD_mm", color = "stim_group_bi",
          palette = c("#00AFBB", "#E7B800"))

cat("GROUPS = Other Med., Nothing\nTIME = Baseline, Year 2\nDV = Length (sec)")
print(summary(aov(Length_sec ~ Time*nonstim_med_bi + Error(factor(id)/Time), data = motion_vars_3_long)))
ggboxplot(motion_vars_3_long, x = "Time", y = "Length_sec", color = "nonstim_med_bi",
          palette = c("#00AFBB", "#E7B800"))

cat("GROUPS = Other Med., Nothing\nTIME = Baseline, Year 2\nDV = Mean FD (mm)")
print(summary(aov(MeanFD_mm ~ Time*nonstim_med_bi + Error(factor(id)/Time), data = motion_vars_3_long)))
ggboxplot(motion_vars_3_long, x = "Time", y = "MeanFD_mm", color = "nonstim_med_bi",
          palette = c("#00AFBB", "#E7B800"))

```

#### Covariate differences between groups
```{r,warning=FALSE,message=FALSE}

#
# Load covariates and test for group differences
#

setwd("/Users/adamkaminski/Desktop/stimproj/data/nda_downloads/")
IQ <- read.csv("nih_toolbox.csv",header=TRUE)
 
# Keep only included subs
IQ <- IQ[IQ$src_subject_id%in%new_overlap,]
IQ$eventname[IQ$eventname=="baseline_year_1_arm_1"] <- 0
IQ$eventname[IQ$eventname=="2_year_follow_up_y_arm_1"] <- 2
IQ <- reshape(IQ, idvar = "src_subject_id", timevar = "eventname", direction = "wide")

# match IDs
demos <- demos[demos$src_subject_id%in%netdat1$src_subject_id,]
demos <- demos[order(demos$src_subject_id),]
IQ <- IQ[IQ$src_subject_id%in%netdat1$src_subject_id,]
IQ <- IQ[order(IQ$src_subject_id),]

if (sum(as.numeric(demos$src_subject_id==netdat1$src_subject_id))==dim(netdat1)[1]) {
  grps <- netdat1[,c(87)]
}
if (sum(as.numeric(IQ$src_subject_id==netdat1$src_subject_id))==dim(netdat1)[1]) {
  demos <- cbind(demos,IQ[,c(2,4,14,16)])
}

# reorder demos, take out sex
sex <- demos$sex
demos <- demos[,c(1,14,12,15,13,11)]

# make temp dfs
grps <- as.data.frame(grps)

if (sum(as.numeric(demos$src_subject_id==netdat1$src_subject_id))==dim(demos)[1]) {
  demos$mean_FD_mm_0 <- netdat1$meanFD.0
  demos$mean_FD_mm_2 <- netdat1$meanFD.2
  demos$length_sec_0 <- netdat1$FD.under.0.2.0
  demos$length_sec_2 <- netdat1$FD.under.0.2.2
}

demos_gm <- demos[(demos$mean_FD_mm_0<0.5&demos$mean_FD_mm_2<0.5),]
grps_gm <- as.data.frame(grps[(demos$mean_FD_mm_0<0.5&demos$mean_FD_mm_2<0.5),])
colnames(grps_gm) <- c("grps")

demo_diffs <- matrix(0,9,4)
row <- 1
for (i in 3:length(demos_gm)) {
    t_out <- t.test(demos_gm[,i]~grps_gm$grps)
    demo_diffs[row,1] <- round(t_out$estimate[2],digits=3)
    demo_diffs[row,2] <- round(t_out$estimate[1],digits=3)
    demo_diffs[row,3] <- round(t_out$statistic,digits=3)
    demo_diffs[row,4] <- round(t_out$p.value,digits=3)
    row <- row + 1
}

rownames(demo_diffs) <- c("Baseline Age (months)","Year 2 Age (months)","Baseline FSIQ","Year 2 FSIQ","SES",
                          "Baseline Mean FD","Year 2 Mean FD","Baseline Length of Data","Year 2 Length of Data")
colnames(demo_diffs) <- c("Medication Group","Naive Group","t statistic","p value")

require(gt)
nice_tab_2 <- gt(as.data.frame(demo_diffs),
   rownames_to_stub = TRUE) |> 
    tab_row_group(
    label = "Stimulant vs. No Stimulant",
    rows = 1:9
  ) |> 
  tab_header(
    title = 'Demographic Differences Between Medication Groups'
    ) |> 
  opt_stylize(style = 3, color = 'gray'
    )
   
nice_tab_2

sex_gm <- sex[(demos$mean_FD_mm_0<0.5&demos$mean_FD_mm_2<0.5)]
sex_diffs <- matrix(0,2,4)
sex_t <- sex[grps_gm$grps!="1"]
temp <- chisq.test(netdat1_gm$sex,grps_gm$grps)
sex_diffs[1:2,1:2] <- temp$observed
sex_diffs[1,3] <- round(temp$statistic, digits=3)
sex_diffs[1,4] <- round(temp$p.value, digits=3)
sex_diffs[2,3:4] <- c("-","-")
colnames(sex_diffs) <- c("Naive","Medication","chi-squared statistic","p value")
rownames(sex_diffs) <- c("F","M")

nice_tab_3 <- gt(as.data.frame(sex_diffs),
   rownames_to_stub = TRUE) |> 
    tab_row_group(
    label = "Stimulant vs. No Stimulant",
    rows = 1:2
  ) |> 
  opt_stylize(style = 3, color = 'gray'
    )
   
nice_tab_3


```
